\maketitle
\makedeclaration

\begin{abstract} % 300 word limit
Topic model has found numerous applications in mining textual data. It is an extremely useful tool for discovering the hidden thematic structure of the news and clustering the news collection in a better organization. Latent Dirichlet Allocation (LDA) model and its extensions are getting the popularity in industrial use such as recommendation system, information retrieval and online advertising. However the vast majority of the models have the assumption of static corpus, especially the static topic models. Although we have noticed that some time-aware topic models have paid attention to streaming corpora which is the predominant type of data for the age of Web 2.0, to the best of our knowledge none has taken authorship information into consideration to explore the topic evolution. In this paper we consider the problem of dynamic topic extraction of news documents, while the temporal dynamics of the streams allow topic distribution to evolve over time. Since we can consider news as a document with underlying topics  and the category information predefined by the editors, we can leverage author-topic model with hierarchical structure and extend it by considering temporal pattern of news to track the time-varying distribution of topics over authors and words. The distribution inference at a certain time point is used as the prior for the next inference and the Bayesian approach allows the evidence obtained from the new streaming news data to change the topic-word and author-topic distribution. We have ran our experiments based on all $36,162$ news published on BBC in the first five months of the year 2016, and our experimental results indicate that our proposed Dynamic Author-Topic model outperforms the other state-of-art static and time-aware topic models in terms of topic extraction, topic generalization measured by perplexity and surely topic evolution. 



\end{abstract}

\begin{acknowledgements}

I would like to pay my best respect to my supervisor Dr. Emine Yilmaz who provides invaluable guidance and support to my research, only with the ongoing creative and solid suggestions from Dr. Emine Yilmaz can I finalize my Msc project. 

I also want to tribute to the Dr. Shangsong Liang, who provides precious help for my mathematical deduction work and experimental implementation.

Last but not least, I would absolutely thank Dr. Sylvia Tippmann from BBC News Lab who not only provides me with valuable real world news data, but also enormous guidance for my project, I will show my best respects to her.
\end{acknowledgements}

\setcounter{tocdepth}{2} 
% Setting this higher means you get contents entries for
%  more minor section headers.

\tableofcontents
\listoffigures
\listoftables

